Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-01 paper/main.tex
some cleaning in discussion

@@

\subsubsection{Events related to high-level perception}

@@

% intro
Lastly, we implemented five contrasts for every stimulus for the purpose of
negative control.
% AV: no_cut > x
In the analysis of the AV data, none of the contrasts that compared the ``no cut
condition''  to a movie cut category (contrasts 6, 7, 8, 9) yielded significant
clusters.
% AV using nouns
The contrast that used the narrator's nouns but in the AV stimulus (se\_new >
se\_old) yielded a significant cluster in the right PPA and bilateral clusters
in the superior lateral occipital cortices (the right hemispheric cluster
extending into the superior parietal cortex).

@@

% previous studies
Previous studies reported bilaterally increased hemodynamic activity in the PPA
when participants were watching static pictures of landscape compared to
pictures of faces or objects (e.g. \citep{epstein1998ppa,
epstein1999parahippocampal}) whereas one study using spoken sentences reported
mixed results \citep{aziz2008modulation}.
% current study: similar
In line with previous studies, we use here also operationalize spatial
perception via general linear model (GLM) $t$-contrasts in two naturalistic
stimuli.
% current study: dissimilar
Contrary to previous studies, our current approach is not based on
carefully designed sets of stimuli but based on annotated stimulus features
incidentially occurring in an audio-visual movie and its audio-description.
% group AV
On a group level, whole brain-analysis results for the movie stimulus show
signifcantly increased hemodynamic activity spatially overlapping with a
traditionally localized PPA but also extending into earlier visual cortices.
% group AD
Results for the audio-description stimulus reveal significant activation
restricted to the anterior part of the PPA.
% individual level
On an individual level, results of the audio-description show significant
bilateral clusters in the anterior PPA of nine subjects and significant
unilateral clusters in two subjects.
% meaning 1
Results suggest that increased activation in the PPA during the perception of
static pictures generalizes to the perception of spatial information embedded in
a movie and an exclusively auditory stimulus.
% meaning 2
Our results provide further evidence that the PPA can be divided into functional
subregions. An auditory narrative might substitute a visual paradigm to localize
the PPAs anterior part in visually impaired subjects.

@@

% intro
First, we analyzed data from the movie stimulus offering ecologically more valid
but still visual stimulation.
%
An early study \citep{bartels2004mapping} that manually annotated the content
(color, faces, language, and human bodies) of movie frames found that
specialization of functional areas is preserved during movie watching.
%
Contrary to \citep{bartels2004mapping}, we categorized the frames after movie
cuts independent of the frames' content.\todo{PPA in
    \citep{hasson2004intersubject} but do reverse ISC}
% hypo
Despite this ``adventurous'' / ad hoc approach, we hypothesized that
[confounding variables could/would average out and] our whole-brain analyses
would lead to significant clusters in the PPA.
% results
Group results of the AV stimulus' primary contrast yielded a clusters that span
the group overlap of individual PPA ROIs from anterior to posterior.
% difference in location/size to AD and VIS
The cluster also extends into medial regions (dorsal precuneus and dorsal
posterior cingulate cortices), and into more posterior regions (occipital
fusiform gyrus and intracalcarine cortex) bilaterally.
% confound of higher perception
The larger extension into more posterior, primary visual areas can be attributed
to the fact that we averaged the content of individual frames after a cut and
did not control for confounding features like depicted faces or objects or
attentional focus of subjects.
%
\todo[inline]{bigger size of clusters is not surprising;  imo still impressive
low amount of random clusters in the brain (and not one third of brain
significant); Clusters in Bartels (2004) are actually kinda big, too;)}
%
Noteworthy, we here exploited a confound in the stimulus structure induced by
cinematographic tendencies (cf. method section;
% a)
a) movies tend to establish the setting and the spatial relationships within a
setting at the beginning of a movie;
% b)
b) the field sizes of movie shots tend to decrease when switching back to
already established settings
% c)
c) shots within a recurring locale or setting tend to shift to depicting persons
and objects \citep{brown2012cinematography, mercado2011filmmakers}.
% interpretation
-> concluding statement?
% shortcomings
Since the capability to isolate clusters or networks correlating with specific
perceptual (or cognitive) processes is influenced by the amount of annotated
stimulus features further studies focusing on visual perception should annotate
and model visual features of naturalistic stimuli more rigorously.
% solution
Future studies that aim to use a movie to localize different visual areas should
extensively annotate the content of frames (e.g. using the open-source solution
``Pliers'' for feature extraction from a visual naturalistic stimulus;
\citep{mcnamara2017developing}) and record the subject's visual attention via
eye-tracking.

\todo[inline]{Nevertheless: that this simple approach works actually suprisingly
well; shows that a lot of confounds average out, since we clusters are not super
big or all over the brain (and that across contrasts)}

\todo[inline]{on the other hand: movies are nice but have idiosyncrasies; so,
maybe you should be aware of these idiosyncrasies (and control for it) in case
you wanna use movies for research}

% summary: nevertheless
\todo[inline]{Summary: so, yes, what is the main message of this
``cross-modal-control-movie-thing''?? cf. intro: ``works'' but clusters more
widespread}

@@

% intro
Second, we analyzed data from the audio-description.
% hypothesis
Encouraged by \citep{aziz2008modulation}, we also hypothesized that spatial
information embedded in an exclusively auditory stimulus would correlate with
increased hemodynamic activity in the PPA.
% results
Group results of the AD stimulus' primary contrast yielded spatially concise
clusters in the anterior part of the PPA group overlap that we gained from a
visual localizer experiment \citep{sengupta2016extension}.
% diff to Aziz (2008)
Unlike \citep{aziz2008modulation} who modeled events from on- to offset of
sentences (describing unknown and famous places and faces), we modeled events
from on- to offset of single words (that indicates the visual content to the
listener).
% conclusion
\citep{aziz2008modulation} found significantly increased activity in only the
left PPA and only for sentences describing famous places compared to famous
faces.\todo{average response across voxels in ROI}
%
Contrary, our group results suggest that auditory spatial information
compared to non-spatial information correlates with bilaterally increased
activation in its anterior.\todo{any concluding statement?}

@@

% optimal stimulus type in vision
In the visual domain, landscapes and not pictures of landmarks or buildings are
considered to be the ``optimal'' stimulus type
\citep{epstein2008parahippocampal}.\todo{a review}
% we did not choose se\_new and se\_old
We did not include the categories that contained switches from one setting to
another (\texttt{se\_new} and \texttt{se\_old}) which one might assume to
contain the auditory equivalent to the ``optimal'' visual stimulus type in the
primary AD contrast.
% why
The reason was that the categories \texttt{se\_new} and \texttt{se\_old} were
heterogeneous: they rarely contained holistic (but also vague) descriptions of
landscapes (e.g.  ``[in a] football stadium'', ``[Forrest is running through
the] jungle'') but mostly landmarks or buildings and also non-spatial hints
(e.g. ``[Jenny as a] teenager``).
% further studies
Given that humans can identify the gist of a rich visual scene within the
duration of a single fixation \citep{henderson2003human} further studies might
investigate if vague verbal descriptions of landscapes lead to a different
hemodynamic activity level than descriptions of more concrete parts of a scene
(e.g.``[a] beacon'', [a] ``farmhouse'').

@@

\todo[inline]{how to discuss Bland-Altman-Plots???; dunno if this is meaningful:
z-scores in the anterior part of PPA are higher in AD contrasts than in contrast
of localizer}
%
Based on the fact that the annotation of nouns still offered a more precise way
to operationalize the perception of spatial information than the annotation of
cuts and locations, we also hypothesized that analyzing the data from the
audio-description could localize the PPA in individual persons.
%
Hence to test if an auditory narrative could [in principle] substitute a visual
localizer experiment, we examined the results from the audio-description's
primary contrast on an individual level.
% results of dedicated localizer
The visual localizer \citep{sengupta2016extension} revealed bilateral ROIs in 12
of 14 subjects and a unilateral right ROI in two subjects (sub-04, sub-20).
%
Whereas \citep{sengupta2016extension} chose the subjectively ``best fitting''
$z$-threshold in an unthresholded $z$-map from one of three contrasts by visual
judgment, we used a ``one threshold fits all approach`` (Z>3.4, p<.05
cluster-corrected).
% in the current study
The audio-description's primary contrast that we used for all subjects yielded
significant bilateral clusters in 9 of 14 subjects (of which sub-04 shows only a
right-lateralized PPA ROI), and a unilateral significant cluster in one subject.
% similar: anterior part
Similarly to the group average results, results on an individual level also
reveal that clusters are spatially restricted to the anterior part of individual
PPAs.
% conclusion
Thus, the increased hemodynamic activity in the anterior part of the PPA
revealed on the group level is not just a by-product of the averaging process
[as it can reliably be found in individual study participants.]
% conclusion
Lastly, our exploratory analysis suggests that a naturalistic auditory stimulus
can [in principle] be applied to localize (the anterior part) of an higher-level
visual area in the majority of subjects.
% one threshold (and contrast) to rule them all
Further studies that aim for individual diagnostics / ROI localization should
nevertheless test more than one contrast to gain the ``best'' individual
ROIs.\todo{..ouff}

@@

% why we did a couple of contrasts
To test the robustness of our approach, we created several additional contrasts
for each naturalistic stimulus by varying the contrasted categories (and thus
the amount of available data), and how well the annotated events within
categories on average matched the stimulus type that we assumed to be
preferentially processed in the PPA.

@@

% PPA AV
Regarding contrasts of the AV stimulus (see Table \label{tab:av-contrasts}), all
five AV contrasts show significant bilateral clusters in the PPA but also
extending into more posterior brain regions.
% PPA AD
Regarding contrasts of the AD stimulus (see Table \label{tab:ao-contrasts}), six
of overall eight contrasts show significant bilateral clusters in the anterior
part of the group PPA overlap.
% results indicate robustness
Thus, the results of the additional contrasts indicate that our findings are
robust and do not depend on the design of one specific contrasts.
% but
Nevertheless, results are sensitive to the contrasted categories and the amount
of available data.
% example
For example, contrast 8 of the AD stimulus (\texttt{se\_new} > texttt{se\_old})
that used the most heterogeneous categories comprising the least amount of
events yielded neither a significant cluster in the right-hemispheric nor
left-hemispheric PPA.
% concluding statement
Hence, investigators using model-driven analyses have to consider how many
events a naturalistic stimulus may provide and how homogeneous the events to be
averaged might be.

@@

% anterior vs posterior pattern
In contrasts 1 to 6 of the AD stimulus, we find consistently significant
clusters spatially constrained to the anterior part of the PPA group overlap as
defined by the visual localizer [as well as constrained to the anterior part of
significant cluster of AV contrasts].
% question
This raises the question if the different activation patterns can be attributed
to different features inherent in visual compared to verbal stimuli.
% visual scenes: probably submodules
In the domain of visual scene perception, previous studies provide evidence that
the PPA can be divided into functionally subregions that might process different
stimulus features.
% posterior: functionality
The posterior PPA (pPPA) is functionally more responsive than the anterior PPA
(aPPA) to low-level features of scenes or (abstract) objects
\citep{baldassano2013differential, nasr2014thinking,
rajimehr2011parahippocampal}.
% anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
% cytoarchitectonic map
The aPPA is functionally more responsive than pPPA to high-level features of
scenes (e.g. real-word size \citep{park2015parametric}; a scene's abstract
identity/category \citep{marchette2015outside, watson2016patterns}) and objects
(e.g. spatial contextual associations \citep{aminoff2007parahippocampal,
aminoff2013role}).
% connectivity
Moreover, pPPA and aPPA show differences in connectivity profiles.
% posterior
The pPPA is more strongly functionally connected to the occipital visual cortex
than the aPPA \citep{baldassano2013differential, baldassano2016two}.
% including lateral occipital cortex (LOC) and transverse occipital sulcus (TOS)
% anterior
The aPPA is more strongly functionally connected to portions of the default mode
network, including caudal inferior parietal lobe (cIPL), the restrosplenial
complex (RSC), medial PFC and the lateral surface of the anterior temporal lobe
\citep{baldassano2013differential, baldassano2016two}.
% conclusion: subregions
According to the hypothesis by \citep{baldassano2013differential} the PPA
consists of subregions that activate selectively to scenes and ``cooperate to
build a complete representation of a scene''.
% Their distinct connectivity properties do suggest that each may be involved in
% specific aspects of visual and cognitive processing involved in the
% overarching goal of scene understanding \citep{baldassano2013differential}.
% The fact that anterior PPA had a lower sensitivity to our abstract object
% stimuli does not necessarily imply that this region does not use object
% information \citep{baldassano2013differential}. Previous work has shown that
% PPA responds to objects that have spatial associations [Aminoff et al. 2007],
% are space-defining [Mullally and Maguire 2011], and are
% navigationally-relevant [Janzen and Van Turennout 2004]. These types of
% responses require spatial memory and cannot be based purely on visual features
% like object shape. \citep{baldassano2013differential}.
Our results add further evidence that the PPA is not a homogeneous area but can
be divided into functionally subregions.
% pPPA
Our results suggest that the pPPA is more concerned with visual aspects immanent
in pictures or movie shots of landscapes.
% aPPA
The aPPA might be more concerned with non-visual aspects of spatial information
(e.g. spatial contextual information \citep{aminoff2013role,
aminoff2015associative, baumann2016functional}) as immanent/inherent in both
visual and verbal stimuli.

@@

\todo[inline]{part regarding RSC \& LOC is now super short; maybe give half a
sentence that this was not focus of the story (but still kinda expected)}

% intro
Apart from the PPA, we find significantly increased activity in the dorsal
precuneus and posterior cingulate region (e.g. retrosplenial cortex; RSC) and
lateral occipital cortex (LOC) across contrasts of both naturalistic stimuli.
% RSC intro
Like the PPA, the RSC (AV stimulus: significant clusters in 3 of 5 contrasts; AD
stimulus: 7 of 8 contrasts) and LOC (AV stimulus: XY of 5 contrasts; AD
stimulus: XY of 8 contrasts) are known to be scene-selective regions (see
\citep{chrastil2018heterogeneity, bettencourt2013role} for reviews).
% conclusion
\todo[inline]{conclusion: what does that say about our results regarding PPA as
a scene-selective region, and audio-visual and auditory naturalistic stimuli in
general?}

\todo[inline]{if we locate a conclusion regarding ``naturalistic stimuli, fuck
yeah'' (+ re-use of existent data) here already, we can add the following part
``not many random clusters'' \& ``control contrasts'' imo elegantly and
shortened here as ``caveats''}

\todo[inline]{``caveats'' = you need extensive annotations and need to know the
    confound structure; but it's the confound structure that leads to the
    hypothesis that changes of the soundscape might also correlate with activity
in the PPA (cf. ``shower thoughts'')}

@@

\subsubsection{not many random cluster}

@@

\todo[inline]{make this short; as expected almost everywhere null results ->
natural stimuli = suitable}

\todo[inline]{similarly: we have a pattern of spatially restricted clusters
across contrasts (and stimuli) in the PPA contrasts -> natural stimuli =
suitable}

% AV: contrast with AV nouns
Compare Figure \ref{fig:reg-corr}: nouns that indicate a change to a new setting
are correlated  with cuts to a new setting (vse\_new; r$\approx$0.3; second
highest correlation of a verbal hint category with a cut category; AND: nouns
that indicate change to a familiar setting are somewhat correlated with cuts to
a familiar setting (se\_old; r$\approx$0.4; highest correlation of a verbal
category with a cut category).

% AD: correlation of these nouns with cuts
Compare Figure \ref{fig:reg-corr}: nouns that indicate change to a new setting
are correlated  with cuts to a new setting (vse\_new; r$\approx$0.3; second
highest correlation of a verbal hint category with a cut category.

\subsubsection{shower thought: changes in soundscape should also correlate with
PPA activity}

Cuts probably correlate with change in soundscape; change in soundscape often
anticipates narrator (would lower detection power) or occurs in parallel with
narrator; cf. correlation of cuts to other setting (independent of familiarity)
with nouns that indicate a change of setting; cf. control contrasts [which
ones?]
% arnott hypothesis
We hypothesize that not just semantic information but also the mere changes of a
soundscape that indicate a setting's spatial layout could correlate with
increased activity in the PPA.
% arnott
\todo[inline]{e.g. arnott2008crinkling finds increased activations in PPA to
sounds made by objects (that reveil object's material/identity)}

>>>>

% \usepackage{helvet}

% \renewcommand{\familydefault}{\sfdefault}

@@

\subsubsection{Events related to high-level perception} \label{rationale}

@@

% intro
Lastly, we implemented five contrasts for every stimulus for the purpose of
negative control.
% AV: no_cut > x
In the analysis of the AV data, none of the contrasts that compared the ``no cut
condition''  to a movie cut category (contrasts 6, 7, 8, 9) yielded significant
clusters.
% AV using nouns
The contrast that used the narrator's nouns but in the AV stimulus
(\texttt{se\_new} > \texttt{se\_old}) yielded a significant cluster in the right
PPA and bilateral clusters in the superior lateral occipital cortices (the right
hemispheric cluster extending into the superior parietal cortex).

@@

% previous studies
Previous studies reported bilaterally increased hemodynamic activity in the PPA
when participants were watching static pictures of landscape compared to
pictures of faces or objects (e.g. \citep{epstein1998ppa,
epstein1999parahippocampal}) whereas one study using spoken sentences reported
mixed results \citep{aziz2008modulation}.
% current study: similar
In line with previous studies, we use here also operationalize spatial
perception via general linear model (GLM) $t$-contrasts in two naturalistic
stimuli.
% current study: dissimilar
Contrary to previous studies, our current approach is not based on carefully
designed sets of stimuli but based on annotated stimulus features incidentially
occurring in an audio-visual movie and its audio-description.
% group AV
On a group level, whole brain-analysis results for the movie stimulus show
signifcantly increased hemodynamic activity spatially overlapping with a
traditionally localized PPA but also extending into earlier visual cortices.
% group AD
Results for the audio-description reveal significant activation in the PPA but
restricted its anterior part.
% individual level
On an individual level, results of the audio-description show significant
bilateral clusters in the anterior PPA of nine subjects and significant
unilateral clusters in one subjects.
% meaning 1
Results suggest that increased activation in the PPA during the perception of
static pictures generalizes to the perception of spatial information embedded in
a movie and an exclusively auditory stimulus.
% meaning 2
Our results provide further evidence that the PPA can be divided into functional
subregions. An auditory narrative might substitute a visual paradigm to localize
the PPAs anterior part in visually impaired subjects.

@@

% intro
First, we analyzed data from the movie stimulus offering ecologically more valid
but still visual stimulation.
%
An early study \citep{bartels2004mapping} that manually annotated the content
(color, faces, language, and human bodies) of movie frames found that
specialization of functional areas is preserved during movie watching.
%
Contrary to \citep{bartels2004mapping} who annotated the movie frames' content
(color, faces, language and human bodies), we categorized each frame after a cut
independent of its content. \todo{PPA in \citep{hasson2004intersubject} but do
reverse ISC; Bartels' clusters are actually pretty big too}
% hypo
Despite this ad hoc approach, we hypothesized that [confounding variables
could/would average out and] our whole-brain analyses would lead to significant
clusters in the PPA.
% results
Group results of the AV stimulus' primary contrast yielded a cluster that span
the group overlap of individual PPA ROIs from anterior to posterior.
% difference in location/size to AD and VIS
The cluster also extends into medial regions (dorsal precuneus and dorsal
posterior cingulate cortices), and into more posterior regions (occipital
fusiform gyrus and intracalcarine cortex) bilaterally.
% confound of higher perception
The larger extension into more posterior, primary visual areas can be attributed
to the averaging process that did not control for confounding visual features or
the attentional focus of study participants.

\todo[inline]{I am pretty surprised the clusters are not all over the brain.  I
do not know where/how do phrase it but should be mentioned imo}

% shortcomings
Since the capability to isolate clusters or networks correlating with specific
perceptual (or cognitive) processes is influenced by the amount of annotated
stimulus features further studies focusing on visual perception should annotate
and model visual features of naturalistic stimuli more rigorously.
% solution
Future studies that aim to use a movie to localize different visual areas should
extensively annotate the content of frames (e.g. using the open-source solution
``Pliers'' for feature extraction from a visual naturalistic stimulus;
\citep{mcnamara2017developing}) and record the subject's visual attention via
eye-tracking.

\todo[inline]{nice that the following is mentioned but what to do with it?
Movies are nice but have idiosyncrasies; so, maybe you should be aware of these
idiosyncrasies (and control for it) in case you wanna use movies for research?}
% exploited cinematographic tendencies
We here exploited a cinematographic confound in the stimulus structure (cf.
\ref{rationale}).
%
Film directors tend to establish the geometry of locations earlier in the movie
and to later focus more on persons and objects relevant to the evolved plot
later  \citep{brown2012cinematography, mercado2011filmmakers}.

% summary: nevertheless
\todo[inline]{Overall summary for AV: so, yes, what is the main message of this
``cross-modal-control-movie-thing''?? cf. intro: ``works'' but clusters more
widespread}

@@

% intro
Second, we analyzed data from the audio-description.
% hypothesis
Encouraged by \citep{aziz2008modulation}, we also hypothesized that spatial
information embedded in an exclusively auditory stimulus would correlate with
increased hemodynamic activity in the PPA.
% diff to Aziz (2008)
\citep{aziz2008modulation} modeled events from on- to offset of sentences
(describing unknown and famous places and faces), and compared activity levels
that were averaged across voxels of ROIs (PPA and fusiform face
\citep{kanwisher1997ffa}) defined by a localizer experiment.
% Aziz results
Study results revealed significantly decreased activity in only the left PPA
compared to activity in the FFA, and only for sentences describing famous places
compared to famous faces.
% we: model & whole brain
Here we modeled events from on- to offset of single words and performed an
whole-brain analysis.
% our results
Group results of audio-description's primary contrast yielded spatially concise
clusters in the anterior part of the PPA group overlap.
% concluding statement
Contrary to \citep{aziz2008modulation}, our group results suggest that auditory
spatial information compared to non-spatial information correlates with
bilaterally increased activation in the anterior part of the PPA.

@@

% optimal stimulus type in vision
In the visual domain, landscapes and not pictures of landmarks or buildings are
considered to be the ``optimal'' stimulus type
\citep{epstein2008parahippocampal}.\todo{a review}
% we did not choose se\_new and se\_old
We did not include the categories that contained switches from one setting to
another (\texttt{se\_new} and \texttt{se\_old}) which one might assume to
contain the auditory equivalent to the ``optimal'' visual stimulus type in the
primary AD contrast.
% why
The reason was that the categories \texttt{se\_new} and \texttt{se\_old} were
heterogeneous: they rarely contained holistic (but also vague) descriptions of
landscapes (e.g.  ``[Forrest is running through the] jungle'') but mostly
landmarks or buildings, and also non-spatial hints (e.g. ``[Jenny as a]
teenager``).
% further studies
Given that humans can identify the gist of a rich visual scene within the
duration of a single fixation \citep{henderson2003human} further studies might
investigate if vague verbal descriptions of landscapes lead to a different
hemodynamic activity level than descriptions of more concrete parts of a scene
(e.g.``[a] beacon'', [a] ``farmhouse'').

@@

\todo[inline]{how to discuss Bland-Altman-Plots???; dunno if this is meaningful:
z-scores in the anterior part of PPA are higher in AD contrasts than in contrast
of localizer}
%
Based on the fact that the annotation of nouns offered a more precise way to
operationalize the perception of spatial information than the annotation of cuts
and locations, we also hypothesized that analyzing the data from the
audio-description could localize the PPA in individual persons.
%
Hence to test if an auditory narrative could [in principle] substitute a visual
localizer experiment, we examined the results from the audio-description's
primary contrast on an individual level.
% results of dedicated localizer
The visual localizer \citep{sengupta2016extension} revealed bilateral ROIs in 12
of 14 subjects and a unilateral right ROI in two subjects (sub-04, sub-20).
%
Whereas \citep{sengupta2016extension} chose the subjectively ``best fitting''
$z$-threshold in an unthresholded $z$-map from one of three contrasts by visual
judgment, we used a ``one threshold fits all approach`` (Z>3.4, p<.05
cluster-corrected) in one contrast.
% in the current study
The audio-description's primary contrast yielded significant bilateral clusters
in 9 of 14 subjects (of which sub-04 shows only a right-lateralized PPA ROI),
and a unilateral significant cluster in one subject.
% similar: anterior part
Similarly to the group average results, results on an individual level also
reveal that clusters are spatially restricted to the anterior part of individual
PPAs.
% conclusion
Thus, the increased hemodynamic activity in the anterior part of the PPA
revealed on the group level is not just a by-product of the averaging process
[as it can reliably be found in individual study participants.]
% conclusion
Lastly, our exploratory analysis suggests that a naturalistic auditory stimulus
can [in principle] be applied to localize (the anterior part) of an higher-level
visual area in the majority of subjects.
% one threshold (and contrast) to rule them all
Further studies that aim for individual diagnostics / ROI localization should
nevertheless test more than one contrast to gain the ``best'' individual
ROIs.\todo{..ouff}

@@

% why we did a couple of contrasts
To test the robustness of our approach, we created several additional contrasts
for each naturalistic stimulus by varying the contrasted categories (and thus
the amount of available data), and how well the annotated events within
categories on average matched a stimulus type that we assumed to correlate with
spatial perception.

@@

% PPA AV
Regarding contrasts of the AV stimulus (see Table \ref{tab:av-contrasts}), all
five AV contrasts show significant bilateral clusters in the PPA but also
extending into more posterior brain regions.
% PPA AD
Regarding contrasts of the AD stimulus (see Table \ref{tab:ao-contrasts}), six
of overall eight contrasts show significant bilateral clusters in the anterior
part of the group PPA overlap.
% results indicate robustness
Thus, the results of the additional contrasts indicate that our findings are
robust and do not depend on the design of one specific contrasts.
% but
Nevertheless, results are sensitive to the contrasted categories and the amount
of available data.
% example
For example, contrast 8 of the AD stimulus (\texttt{se\_new} > \texttt{se\_old})
that used the most heterogeneous categories comprising the least amount of
events yielded neither a significant cluster in the right-hemispheric nor
left-hemispheric PPA.
% concluding statement
Hence, investigators that use model-driven analyses have to consider how many
events a naturalistic stimulus may provide and how homogeneous the events to be
averaged might be.

@@

% anterior vs posterior pattern
In contrasts 1 to 6 of the AD stimulus, we find consistently significant
clusters spatially constrained to the anterior part of the PPA group overlap.
% question
This raises the question if the different activation patterns can be attributed
to different features inherent in visual compared to verbal stimuli.
% visual scenes: probably submodules
In the domain of visual scene perception, previous studies provide evidence that
the PPA can be divided into functionally subregions that might process different
stimulus features.
% posterior: functionality
The posterior PPA (pPPA) is functionally more responsive than the anterior PPA
(aPPA) to low-level features of scenes or (abstract) objects
\citep{baldassano2013differential, nasr2014thinking,
rajimehr2011parahippocampal}.
% anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
% cytoarchitectonic map
The aPPA is functionally more responsive than the pPPA to high-level features of
scenes (e.g. real-word size \citep{park2015parametric}; a scene's abstract
identity/category \citep{marchette2015outside, watson2016patterns}) and objects
(e.g. spatial contextual associations \citep{aminoff2007parahippocampal,
aminoff2013role}).
% connectivity
Moreover, pPPA and aPPA show differences in connectivity profiles.
% posterior
The pPPA is more strongly functionally connected to the occipital visual cortex
than the aPPA \citep{baldassano2013differential, baldassano2016two}.
% including lateral occipital cortex (LOC) and transverse occipital sulcus (TOS)
% anterior
The aPPA is more strongly functionally connected to portions of the default mode
network, including caudal inferior parietal lobe (cIPL), the restrosplenial
complex (RSC), medial PFC and the lateral surface of the anterior temporal lobe
\citep{baldassano2013differential, baldassano2016two}.
% conclusion: subregions
According to the hypothesis by \citep{baldassano2013differential} the PPA
consists of subregions that activate selectively to scenes and ``cooperate to
build a complete representation of a scene''.
% Their distinct connectivity properties do suggest that each may be involved in
% specific aspects of visual and cognitive processing involved in the
% overarching goal of scene understanding \citep{baldassano2013differential}.
% The fact that anterior PPA had a lower sensitivity to our abstract object
% stimuli does not necessarily imply that this region does not use object
% information \citep{baldassano2013differential}. Previous work has shown that
% PPA responds to objects that have spatial associations [Aminoff et al. 2007],
% are space-defining [Mullally and Maguire 2011], and are
% navigationally-relevant [Janzen and Van Turennout 2004]. These types of
% responses require spatial memory and cannot be based purely on visual features
% like object shape. \citep{baldassano2013differential}.
Our results add further evidence that the PPA is not a homogeneous area but can
be divided into functionally subregions.
% pPPA
Our results suggest that the pPPA is more concerned with visual aspects immanent
in pictures or movie shots of landscapes.
% aPPA
The aPPA might be more concerned with non-visual aspects of spatial information
(e.g. spatial contextual information \citep{aminoff2013role,
aminoff2015associative, baumann2016functional}) as immanent/inherent in both
visual and verbal stimuli.

@@

\todo[inline]{this part is now super short}

% intro
Apart from the PPA, we find significantly increased activity in the dorsal
precuneus and posterior cingulate region (e.g. retrosplenial cortex; RSC) and
lateral occipital cortex (LOC) across contrasts of both naturalistic stimuli.
% RSC intro
Like the PPA, the RSC (AV stimulus: significant clusters in 3 of 5 contrasts; AD
stimulus: 7 of 8 contrasts) and LOC (AV stimulus: 4 of 5 contrasts; AD stimulus:
unilateral in 2, bilateral in 4 of 8 contrasts) are known to be scene-selective
regions (see \citep{chrastil2018heterogeneity, bettencourt2013role} for
reviews).
% conclusion

@@

\todo[inline]{hm, so why did I build contrasts of the no\_cut condition compared
to the movie cuts categories????}

The four control contrasts of the AV stimulus that compared the
\texttt{no\_cuts} to categories of movie cuts all lead to null results.

% AD anno in AV data
The AV contrast using nouns (\texttt{se\_new} > \texttt{se\_old}): PPA
(unilateral), LOC (bilateral); These noun categories show highest correlation
among nouns with their cut counterpart \texttt{se\_new} (nouns) is r$\approx$0.3
correlated with \texttt{vse\_new} (cuts); \texttt{se\_old} (nouns) is
r$\approx$0.4 correlated with \texttt){vse\_old}.

% AV anno in AV data
The the 5 AV PPA contrasts but with the AV data using cuts. All null results
except:
% contrast 9
vse\_new > pe\_old (conrast 9): left inferior prefrontal cortex (pars
triangularis) and right ventral precuneus/posterior cingulate gyrus.
% contrast 12
vse\_new > vse\_old, vpe\_old (contrast 12): one cluster in the right posterior
hippocampus.

\todo[inline]{shower thought: changes of a soundscape that indicate a setting's
    spatial layout could correlate with increased activity in the PPA
    (arnott2008crinkling finds increased activations in PPA to sounds made by
    objects (that reveil object's material/identity); but at the moment when
    looking at the data I see no systematic in the results that let me assume
that}

\subsubsection{not many random cluster + naturalistic stimuli are cool}

@@

\subsubsection{naturalistic stimuli + data re-use, fuck yeah}

lore ipsum
